New lower bounds for Schur and weak Schur numbers

### 2021-04-09 article/article.tex

This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
5-subsets partition. The new lower bounds includes\(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).

@@

\par
The fifth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.
However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
potential. For example, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
of \(n\). This could be the subject fo a future work. Nevertheless, it would not help for the smallest values.

>>>>

This paper offers new lower bounds for both Schur and weak Schur numbers. These results were produced by pushing forward
Rowley's "templates"-based approach for Ramsey and Schur numbers in 2020. Finding suitable templates allows us to apply Rowley's construction 
to get explicit partitions improving lower bounds. Furthermore, this paper tries to analyse former work on the subject based on
the principle that good partitions into \(n+1\) subsets start with good partitions into \(n\) subsets. We show that exceeding
the previous lower bound \(WS(6) \geqslant 582\) is impossible with such a method upon imposing certain conditions on the good
5-subsets partition. The new lower bounds includes \(S(9) \geqslant 17803\), \(S(10) \geqslant 60948\), \(WS(9) \geqslant 22536 \) and \(WS(10) \geqslant 71214 \).

@@

\par
The fourth section gives new insight on the method that was formerly used to achieve new lower bounds. The principle behind it
might have discarded many interesting partititions of the search space and lowered the highest value that can be reached within it.
However, algorithms based on randomness such as Monte-Carlo algorithms may appear very useful if used in a search space with more
potential. For example, such an algorithm could be used to find better templates and improve inequalities and lower bounds for high values
of \(n\). This could be the subject fo a future work. Nevertheless, it would not help for the smallest values.
